---
title: "Data Science"
author: "Gurleen Kaur"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(tidyverse)
```

Importing dataset in the R.

```{r}
#reading the data
Shopify <- read.csv("Shopify.csv")
#structure of data set
glimpse(Shopify)
mean(Shopify$order_amount)
```

Earlier, we were calculating AOV by taking average of order amount and not considering the number of orders. 
Average order value is the mean amount spent by the customer on a order. On dividing total revenue generated by the business by total number of orders it received, we will get average amount spent by the customer on a order. 

```{r}
Total_Revenue <- sum(Shopify$order_amount)
Total_Revenue
Total_Orders <- sum(Shopify$total_items)
Total_Orders
```

Now that we have total revenue generated  and total orders we can calculate average order value.

```{r}
Average_order_value <- Total_Revenue/Total_Orders
Average_order_value
```

